### 2016-07-05 intro.tex
responding to JK's comments
new related work

First, we note that the security notion forbids~$A$ to win if it
outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
false positive. 
\jnote{We discussed this on the phone, but let me
put it in writing here. I think this is actually a reasonable choice
because it captures the notion that ``even after finding some false
positives, it remains hard to find additional false positives.''
Note that in practice finding false positives is ``easy'' since
$\epsilon$ might be $1/1000$ rather than negligible.} 
\tsnote{For me the question is: is security violated once the first FP is found, or
the second?  My answer, which is in line with the traditional
soundness notion, is that the first FP is a security violation
even if finding it isn't ``hard'' by cryptographic standards.
But I do appreciate your point.  A natural goal is to say that, in some sense,
\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
to what, though?  In the traditional notion, $x$~is picked before the
coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
are sampled.  The direct non-adaptive generalization is to say that
$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
but \emph{not} (directly) to the input-output behaviors of the hash
functions.  The three notions I've proposed in Figure 1 cover a
spectrum adaptivity: the first is adapting to set-membership queries
only, the second to those and hash input-output behavior, the third to
set-membership queries and full knowledge of the hash functions.  Each
has it's own associated (informal) security interpretation.}
\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
that that the adversary wins iff it outputs~$f$ FPs (these may have
been previously queried to the set-membership oracle).  
Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
require~$f$ times the work.  Right?} 
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; 
\jnote{I think this is also reasonable; typically
security is defined without regard for efficiency}
\tsnote{My complaint isn't about efficiency. It's about the fact that,
by not including $|M|$ in the definition, the trivial scheme I give
(just below) is allowed, and is secure.  Anyway, as I say at the end
of this paragraph, this is a small(er) complaint that what follows}. The surrounding
text does say that $\mathbf{B}_1$ ``outputs a compressed
representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
but what exactly this means is never addressed.  The formal syntax
admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints.  But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

@@

We generalize this syntax to hash-based filters that are mutable
\jnote{I find ``mutable'' a slightly awkward term,  maybe because it
makes me think of mutability in the context of programming
languages. In much data structures literature, this is called the
``dynamic'' case, in contrast to the ``static'' case.} \tsnote{I
adopted this term after reading it in some bloom filter
paper(s). Ironically, I liked it for the same reason you think it is
awkward :)  My PL association to the term is that an immutable object
is one whose state cannot be modified after it is created, and a
mutable object is the opposite.  ButI don't really care too much.}, in the sense
that they allow for updating of the representation. This allows us
to capture counting Bloom filters, spectral Bloom filters, stable
Bloom filters, count-min sketches, and other compact set
representation data structures...

@@

\heading{Related work. }
\begin{itemize}
\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.  Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.   If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive. (You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.)  Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.  (Also, since $n=100$ the expected number of trials is roughly $2^{28}$.)  With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.  Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter. Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform. }
\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}

>>>>

First, we note that the security notion forbids~$A$ to win if it
outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
false positive. 
\jnote{We discussed this on the phone, but let me
put it in writing here. I think this is actually a reasonable choice
because it captures the notion that ``even after finding some false
positives, it remains hard to find additional false positives.''
Note that in practice finding false positives is ``easy'' since
$\epsilon$ might be $1/1000$ rather than negligible.} 
\tsnote{For me the question is: is security violated once the first FP is found, or
the second?  My answer, which is in line with the traditional
soundness notion, is that the first FP is a security violation
even if finding it isn't ``hard'' by cryptographic standards.
But I do appreciate your point.  A natural goal is to say that, in some sense,
\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
to what, though?  In the traditional notion, $x$~is picked before the
coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
are sampled.  The direct non-adaptive generalization is to say that
$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
but \emph{not} (directly) to the input-output behaviors of the hash
functions.  The three notions I've proposed in Figure 1 cover a
spectrum of adaptivity: the first is adapting to set-membership queries
only, the second to those and hash input-output behavior, the third to
set-membership queries and full knowledge of the hash functions.  Each
has it's own associated (informal) security interpretation.}

\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
that that the adversary wins iff it outputs~$f$ FPs (these may have
been previously queried to the set-membership oracle).  
Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
require~$f$ times the work.  Right?} 
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; 
\jnote{I think this is also reasonable; typically
security is defined without regard for efficiency}
\tsnote{My complaint isn't about efficiency. It's about the fact that,
by not including $|M|$ in the definition, the trivial scheme I give
(just below) is allowed, and is secure.  Anyway, as I say at the end
of this paragraph, this is a small(er) complaint than what follows}. The surrounding
text does say that $\mathbf{B}_1$ ``outputs a compressed
representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
but what exactly this means is never addressed.  The formal syntax
admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints.  But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

@@

We generalize this syntax to hash-based filters that are mutable
\jnote{I find ``mutable'' a slightly awkward term,  maybe because it
makes me think of mutability in the context of programming
languages. In much data structures literature, this is called the
``dynamic'' case, in contrast to the ``static'' case.} \tsnote{I
adopted this term after reading it in some bloom filter
paper(s). Ironically, I liked it for the same reason you think it is
awkward :)  My PL association to the term is that an immutable object
is one whose state cannot be modified after it is created, and a
mutable object is the opposite.  But I don't really care too much.}, in the sense
that they allow for updating of the representation. This allows us
to capture counting Bloom filters, spectral Bloom filters, stable
Bloom filters, count-min sketches, and other compact set
representation data structures...

@@

\heading{Related work: attacks}
\begin{itemize}
\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\end{itemize}

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\end{itemize}

\heading{Related work: constructions}
\begin{itemize}
\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.  Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.   If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive. (You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.)  Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.  (Also, since $n=100$ the expected number of trials is roughly $2^{28}$.)  With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.  Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter. Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform. }
\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
\item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.  No clear statement of the problem that is being solved.}
\end{itemize}

\heading{Related work: tangential}
\begin{itemize}
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}
